%------------------------
% Alastor Curns Resume
% Written in LateX
%------------------------

\documentclass[letterpaper,11pt]{article}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}
% \usepackage[OT1]{fontenc}

% \usepackage{pandora}
% \usepackage[T1]{fontenc}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% \usepackage{fontspec}
\usepackage[margin=.5in,top=.3in,bottom=.3in,nohead]{geometry}
%\usepackage[margin=1in]{geometry}
\usepackage{latexsym}
%\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{changepage}
\usepackage{textcomp}
\input{glyphtounicode}

%\linespread{.5}

\setlength{\footskip}{4.08003pt}
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.75in}
%\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength\parindent{10pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Commands

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% tilde
\newcommand{\mytexttilde}{\raisebox{0.5ex}{\texttildelow}}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeBigHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\normalsize#3} & \textit{\normalsize#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.08in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeJobBlockStart}{\item\begin{adjustwidth}{.5em}{0em}}
\newcommand{\resumeJobBlockEnd}{\end{adjustwidth}}
\newcommand{\resumeTextBlock}[1]{\small {#1 \vspace{-1pt}}}

\newcommand{\test}{\begin{tabular}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}
\newcommand{\resumeItem}[1]{
    \item\normalsize{
       {#1 \vspace{0pt}}
    }
}

\newcommand{\resumeHeading}[2]{
    \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingWithFootnote}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \vspace{0pt} \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\boldSubjectWithDesc}[2]{
  \normalsize{\textbf{#1}{: #2 \vspace{-2pt}}}
}

\newcommand{\boldSubjectColonWithDesc}[2]{
  \normalsize{\textbf{#1}{: #2 \vspace{-2pt}}}
}

% ----------------------------

\begin{document}
% ------------------ HEADER
\begin{center}
  \textbf{\Huge Alastor Curns} \\ \vspace{2pt}
  \faMobile \hspace{.5pt} \href{tel:16786285085}{678-628-5085}
  $|$
  \href{mailto:alastor.cu@gmail.com}{alastor.cu@gmail.com}
  $|$
  \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/alastorc}{LinkedIn}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/alastor-lee}{GitHub}
  $|$
  \faShield \hspace{.5pt} Secret
  $|$
  \faGlobe \hspace{.5pt} \href{https://maps.app.goo.gl/CdQMUuxD24zfLjYq7}{Oakland, CA}
  $|$
  \faHistory \hspace{.5pt} 9 Years
\end{center}

%--------- Introduction ---------
\section{Introduction}
\resumeSubHeadingListStart
\item{
            Engineering leader of a team of 5, with over 9 years of experience in a range of engineering roles, from junior to lead to architect.
            I spent my initial years in tech developing for various internal projects and traveling to understand customer needs of our platform.
            In 2020, I pivoted to building the new core products of the company in an attempt to modernize. 
            I expanded into new languages and architectures while improving my communication, mentorship, leadership skills.
            I currently work closely with my engineering team to build the product while bridging gaps between design, product, sales, and engineering.
            My focus has always been on practical, pragmatic software solutions.
      }
\resumeSubHeadingListEnd
%--------- Experience -------------
\section{Experience}
\vspace{2pt}
\resumeSubHeadingListStart
\resumeHeading{\normalsize{CodeMettle}}{\normalsize{Atlanta, GA}}
\resumeSubheading{Engineering Manager}{2025 - Present}
\resumeItemListStart
\resumeItem{
  \boldSubjectWithDesc{Responsibility}{
    Take on a heightened role to better influence leadership on engineering decisions and advocate for engineers.
    Balance technical leadership with people development and product decisions.
  }
}
\resumeItem{
  \boldSubjectWithDesc{AI}{
    Learn and teach appropriate use of AI tools like Claude Code, emphasizing interrogation, iteration, and a test-driven style of development.
    Build on skills and MCP servers to improve DevEx.
  }
}
\resumeItemListEnd
\resumeSubheading{Lead Software Engineer}{2020 - Present}
\resumeItemListStart
\resumeItem{
  \boldSubjectWithDesc{Lead}{
    Commit high-quality systems and code while working with the engineering teams towards similar goals.
    Coordinate across engineering and product to design and implement the roadmap and architecture.
  }
}
\resumeItem{
  \boldSubjectWithDesc{Develop}{
    Worked primarily in a Node.js stack (front and backend) with an emphasis on immutability.
    Maintained a Scala/Java polling service.
    Experience using and building complex graphing data structures, concurrent thread management, and good pattern design.
  }
}
\resumeItem{
  \boldSubjectWithDesc{Mentor}{
    Continuously provide feedback and resources like onboarding documentation to new engineers.
  }
}
\resumeItemListEnd
\resumeSubheading{Systems Engineer}{2017-2020}
\resumeItemListStart
\resumeItem{
  \boldSubjectWithDesc{Fullstack Environment}{
    Adapted to novel responsbilities and short deadlines by learning to create and write improved services, backend business logic, APIs, and visualizations in different stacks.
    Leveraged an understanding of the products and pipelines to bridge the gap between product, design, integrators and end-users.
  }
}
\resumeItem{
  \boldSubjectWithDesc{Travel (\mytexttilde30\%)}{
    Visited global customer sites to prototype, demonstrate features, and communicate as the engineering subject matter expert.
  }
}
\resumeItemListEnd
\resumeSubheading{Project Engineer}{August 2016-2017}
\resumeItemListStart
\resumeItem{
  \boldSubjectWithDesc{Project Lead}{Deployed production ready systems to customers while leading a small teams of developers.}
}
\resumeItem{
  \boldSubjectWithDesc{Hardware Integration}{Translated live data from satellite infrastructure into well-defined databases, using Python.}
}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------- Projects --------------
\section{Projects}
\resumeSubHeadingListStart
\item{
            \boldSubjectWithDesc{Polling Backend}{
              Architected asynchronous subprocesses in a Node backend to manage high loads of incoming device data via various protocols (ssh, snmp, http, streaming, serial, tcp, udp, and websocket.)
            }

            \boldSubjectWithDesc{Flows}{Developed a domain specific language and event driven architecture to allow users to define secure polls, data transformation/validation, and rules.}

            \boldSubjectWithDesc{Data Visualizations}{
              Led teams across products to develop geographical and logical graphs with D3, MapBox, cytoscape.js, and reactflow. Wrote datasource plugins for Grafana to hook into Apache Solr and MongoDB.
            }

            \boldSubjectWithDesc{Network Infrastructure}{Created and maintained iOS and Juniper configurations. Built scripts and automations to help manage a network stack for the office. Helped developers and QA setup testing scenarios.}

            \boldSubjectWithDesc{FIPS}{Integrated OpenSSL and BouncyCastle into Node and Java applications for FIPS compliance.}
      }
\resumeSubHeadingListEnd

%-------- Skills --------------
\section{Skills}
\resumeSubHeadingListStart
\item{
            \boldSubjectWithDesc{Languages \& Libraries}{TypeScript, Python, Java, Bash, C, HTML/CSS/JS, \href{https://github.com/Effect-TS/effect}{Effect-TS}, Express, Vite, Gulp}

            \boldSubjectWithDesc{Technologies \& Frameworks}{Node.js, React, Jest, SNMP, Linux, OpenAPI, REST, MongoDB, MUI, Docker, Electron}

            \boldSubjectWithDesc{Methods}{Git, Neovim, Agile, OOP, Functional, Immutable, CI/CD, Claude Code, Snyk, Trivy, Obsidian, Monorepo}
      }
\resumeSubHeadingListEnd

%----------- EDUCATION -----------
\section{Education}
\vspace{2pt}
\resumeSubHeadingListStart
\resumeSubheadingWithFootnote
{Georgia State University}{Atlanta, GA}
{Bachelor of Science in Computer Science; Dean's List; GPA: 3.43}{Graduated May 2015}
\resumeSubHeadingListEnd

\end{document}